Lab2

### 2021-07-29 src/data/DataCleaning.Rmd
cleaned trip distance

```{r read in data, echo=FALSE}
d_covid <- read.csv(url('https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties-recent.csv'))
d_openings <- read.csv(file = './../../data/raw/COVID-19 US state policy database (CUSP) - Closures & Reopening.csv')
d_trips <- read.csv(file = './../../data/raw/Trips_by_Distance_-_2020.csv')

```

```{r filter parameters, echo=FALSE}
# state(s) under investigation
state_id = c("OH","Ohio",39)

@@

# filters by date/state
d_trips <- d_trips %>%
  filter(d_trips, 
         Date >= "4/1/2020", Date <= "4/2/2020",
         grepl(paste(state_id, collapse = "|"), State.Postal.Code)
         )

# cleaning
d_trips_filter <- d_trips %>%

  mutate(County.Name = gsub("([A-Za-z]+).*", "\\1", County.Name)) %>%
  group_by(County.Name) %>%
  rowwise() %>%
  mutate(
    # clean county name format
    County.Name = gsub("([A-Za-z]+).*", "\\1", County.Name),
    # total pop
    total_pop = sum(c_across(Population.Staying.at.Home:Population.Not.Staying.at.Home)),
    # define long trips per capita
    long_trip = sum(c_across(Number.of.Trips.100.250:Number.of.Trips...500)),
    long_trips_pc = long_trip/total_pop,
    # # define short trips per capita
    short_trip = sum(c_across(Number.of.Trips.1.3:Number.of.Trips.50.100)),
    short_trips_pc = short_trip/total_pop
    # #
  ) %>%
  rename(
    state = State.Postal.Code,
    county = County.Name
  ) %>%
  select(
    county, state, total_pop, long_trip, long_trips_pc, short_trip, short_trips_pc
  ) %>%
  distinct(county, .keep_all = TRUE)

  # filter(State.Postal.Code %in% c(state[1]))

  # filter(State.Postal.Code %in% c("AL"), grepl("Aut",County.Name))

trips_col <- ddply(d_trips, "County.Name", numcolwise(sum))

#clean county name format
trips_col$county <- gsub("([A-Za-z]+).*", "\\1", trips_col$County.Name)

#code to merge state info to d
d <- merge(x = trips_col, y = covid_col, by = "county")
d <- merge(x = d, y = d_trips[ , c("county", "State.Postal.Code")], by = "county", all.x=TRUE)

>>>>

```{r read in data, echo=FALSE}
d_covid <- read.csv(url('https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties-recent.csv'))
d_openings <- read.csv(file = './../../data/raw/COVID-19 US state policy database (CUSP) - Closures & Reopening.csv')
d_trips <- read.csv(file = './../../data/raw/Trips_by_Distance.csv')
```

```{r filter parameters, echo=FALSE}
# state(s) under investigation
state_id = c("TX","Texas")

@@

# filters by date/state
d_trips <- d_trips %>%
  mutate(
    Date = as.Date(Date)
  ) %>%
  filter(
    Date >= start_date, Date <= end_date,
    grepl(paste(state_id, collapse = "|"), State.Postal.Code)
  )

# cleaning
d_trips <- d_trips %>%
  # clean county name format
  mutate(
    County.Name = gsub("([A-Za-z]+).*", "\\1", County.Name),
    total_pop = select(.,Population.Staying.at.Home:Population.Not.Staying.at.Home) %>% rowSums(na.rm = TRUE)
    ) %>%
  group_by(County.FIPS) %>%
  mutate(
    # define long trips
    long_trip = sum(c_across(Number.of.Trips.100.250:Number.of.Trips...500)),
    long_trip_pc = long_trip/total_pop,
    # define short trips
    short_trip = sum(c_across(Number.of.Trips.1.3:Number.of.Trips.50.100)),
    short_trip_pc = short_trip/total_pop
  ) %>%
  rename(
    state = State.Postal.Code,
    county = County.Name
  ) %>%
  select(
    county, County.FIPS, state, total_pop, long_trip, long_trip_pc, short_trip, short_trip_pc
  ) %>%
  distinct(County.FIPS, .keep_all = TRUE)
```

```{r merged dataframe, echo=FALSE}
#code to merge state info to d
d <- merge(x = trips_col, y = covid_col, by = "county")
d <- merge(x = d, y = d_trips[ , c("county", "State.Postal.Code")], by = "county", all.x=TRUE)
